---
title: "covid 19"
author: "JONATHAN PAUL P CLAVIO"
date: "20 OCT 20"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent

```{r}
barchartGC(~result + Sex,data=kRdata,type="frequency", main ="Frequency Bar Chart")
```

  
### this bar chart is displaying in total frequency terms our data.  Clearly there are a lot less dead people than alive people as is reflected by the sizes of the bars in the display.  


```{r}
barchartGC(~result + Sex,data=kRdata,type="percent", main ="Percent Bar Chart")
```

### This bar chart is displaying in percent. If there were no difference between alive and dead, the bar chart should be equal, however the opposite is happening. The males are dying close to double than women. More so, more women are alive with the virus than men.


  
## Numerical results

```{r}
table1 <- xtabs(~result + sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

### Looking at our numerical data results, it tells us that 56% of females are alive compared to 44% of males. Looking at the dead, males almost double female in death by 64% and only 36% of females died. 

### Percentage wise, 98.7% of the female population are alive and 97% of the male population are alive. Males are double in the death catagory compared to females.  


## Inferential results 




## Conclusions

